Study of Intra- and Inter-Job Interference on Torus Networks

### 2016-07-13 discussion.tex
pass on discussion

The results shown in the previous section provide insights 
for the design of smart and flexible job placement policy. 
By scrutinizing job's communication behavior, 
we can identify job's dominant communication pattern 
and pinpoint the ``neighborhood communication". 
With such knowledge about jobs' communication patterns, 
we can analyze the possible interference between jobs and 
take precautions to alleviate the negative effect when making placement decisions.

When an application with dominant communication that is intensive many-to-many, 
the scheduler should provide it with compact node allocation and exclusive network provision. 
The compact allocation can guarantee the shortest pair-wise distance between all the ranks, 
and make the data transfer between ranks take less hops. 
On the other hand, 
the exclusive network provision will prevent other adjacent applications from sharing network resources, 
thus eliminate the performance degradation due to interference.

Not every application's preferable resource are compact allocation 
and exclusive network provision. 
As we demonstrate in our study, 
applications whose dominant communication pattern contains intensive 
``neighborhood communication" like nearest Neighbor do not benefit 
from compact allocation and exclusive network provision. 
Applications, such as AMG, can run with non-contiguous node 
allocation without performance degradation, 
as long as the allocation unit can accommodate their ``neighborhood communication".

The size of allocation unit shouldn't be fixed. 
Instead, the scheduler should choose a proper unit size 
based on the scale of ``neighborhood communication" of each job. 
The best unit size should be neither too big nor too small, 
just perfectly fit for the scale of that ``neighborhood". 
Big unit size can not be fully utilized and thus cause fragmentation. 
Small unit size will not be able to accommodate the ``neighborhood communication", 
making the intra-job communication less efficient.

The advantage of making job placement with consideration about job's communication pattern is obvious. 
First, compared with contiguous allocation policy, 
the new scheduler with job's communication pattern awareness can be more flexible, 
without requiring the system to provide a big contiguous partition to accommodate the whole application, 
it only needs to provide a small set of compact nodes that is 
sufficient for all the "local community" in the application. 
On the other hand, 
the new scheduler is able to preserve the locality of application's communication pattern. 
Indeed, the small compact node set (allocation unit) provided for the application's 
``local communities" can preserve the communication locality in the maximum extent. 
The design of such a new scheduler with job communication pattern awareness 
is part of our future work.

>>>>

The results shown in the previous sections provide insights 
for the design of a smart and flexible job placement policy. 
By scrutinizing the communication behavior of jobs, 
we can identify their dominant communication patterns 
and pinpoint locality needs. 
With such knowledge about communication patterns, 
we can analyze the possible interference between jobs and 
take precautions to alleviate interference when making placement decisions.

When an application with intensive many-to-many communication is submitted to the system, 
the scheduler should provide it with compact node allocation and exclusive network resources. 
Compact allocation can guarantee the shortest pair-wise distance between all the ranks. 
Additionally, the exclusive network provision will prevent other jobs from sharing network resources, 
thus eliminating the performance degradation due to interference.

Not every application requires compact allocation and exclusive network provisioning. 
As we demonstrate in our study, 
applications whose dominant communication pattern contains intensive 
``neighborhood communication" like nearest neighbor may not benefit 
from compact allocation and exclusive network provision. 
Applications, such as AMG, can run with non-contiguous node 
allocation without significant performance degradation, 
as long as the allocation unit can accommodate their rank-rank locality.

The size of allocation unit shouldn't be fixed. 
Instead, the scheduler should choose a proper unit size 
based on the granularity of communication locality of each job.   
Large unit sizes can not be fully utilized and thus cause fragmentation. 
Small unit sizes will not be able to accommodate the communication locality, 
resulting in less efficient intra-job communication.

The advantage of performing job placement with consideration 
of job communication patterns is straightforward,
given our experimental analyses. 
Compared with contiguous placement policy, 
schedulers with communication pattern awareness can be more flexible, 
relaxing the need to provide contiguous partitions to accommodate the whole application,
avoiding fragmentation issues inherent in contiguous placement.
Indeed, smaller compact node sets (allocation units) provided for application's
``local communication" can help preserve the communication performance to a sufficient extent. 
The design of such a new scheduler with job communication pattern awareness 
is part of our future work.
